Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
Changes to origin definitions

\begin{defn}{(Origin)}
  In $N$-dimensions, the \emph{origin} $\mathbf{0}_N$ is the singleton set
  $\{0^N\}$, or equivalently the vector of unit intervals $\interv{0}{0}{N}$.
\end{defn}

\begin{defn}{(Extended origin)}
  In $N$-dimensions, the \emph{extended origin} is the interval
  $\interv{-1}{1}{N}$ which is a subset of \region{N}.
\end{defn}

>>>>

\todo{%
  Definition of origin is not needed.

  \begin{defn}{(Origin)}
    In $N$-dimensions, the \emph{origin} $\mathbf{0}_N$ is the singleton set
    $\{0^N\}$, or equivalently the vector of unit intervals $\interv{0}{0}{N}$.
  \end{defn}
}

\begin{defn}{(Extended origin)}
  In $N$-dimensions, the \emph{extended origin} is the interval
  $\interv{-1}{1}{N}$ contained in \region{N}.
\end{defn}
